---
title: "p8105_hw6_zl2746"
author: "Ze Li"
date: "2023-11-27"
output: github_document
---

```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(rvest)
library(ggplot2)
library(broom)
library(p8105.datasets)
library(modelr)

set.seed(1)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
weather_df
```

```{r}
# Plot simple linear regression with tmax as the response 
# with tmin and prcp as the predictors
weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_smooth() +
  geom_point()

weather_df |> 
  ggplot(aes(x = prcp, y = tmax)) + 
  geom_smooth() +
  geom_point()
```


```{r}
model_slr1 = lm(tmax~tmin, weather_df)
summary(model_slr1)
model_slr2 = lm(tmax~prcp, weather_df)
summary(model_slr2)
```


Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities. Plot the distribution of your estimates, and describe these in words.

Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r̂ 2 and log(β̂ 0∗β̂ 1). 

* tmax as the response & tmin as the predictors

```{r}
# Start with a lil function
boot_sample = function(df) {
  
  sample_frac(df, replace = TRUE)
  
}

# Draw 5000 samples and analyze them
# Do the lm fit.
boot_results = 
  tibble(strap_number = 1:5000) |> 
  mutate(
    strap_sample = map(strap_number, \(i) boot_sample(weather_df)),
    models = map(strap_sample, \(df) lm(tmax ~ tmin, data = df)),
    results = map(models, broom::tidy)
  ) |> 
  select(strap_number, results) |> 
  unnest(results)

# try to summarize these results – get a bootstrap SE
boot_results |> 
  group_by(term) |> 
  summarize(
    se = sd(estimate)
  )

# look at the distribution
boot_results |> 
  filter(term == "tmin") |> 
  ggplot(aes(x = estimate)) + 
  geom_density()

# construct a CI
boot_results |> 
  group_by(term) |> 
  summarize(
    ci_lower = quantile(estimate, 0.025),
    ci_upper = quantile(estimate, 0.975)
  )
```

* tmax as the response & prcp as the predictors

```{r}
# Draw 5000 samples and analyze them
# Do the lm fit.
boot_results2 = 
  tibble(strap_number = 1:5000) |> 
  mutate(
    strap_sample = map(strap_number, \(i) boot_sample(weather_df)),
    models = map(strap_sample, \(df) lm(tmax ~ tmin + prcp, data = df)),
    results = map(models, broom::tidy)
  ) |> 
  select(strap_number, results) |> 
  unnest(results)

# try to summarize these results – get a bootstrap SE
boot_results2 |> 
  group_by(term) |> 
  summarize(
    se = sd(estimate)
  )

# look at the distribution
boot_results2 |> 
  filter(term == "tmin") |> 
  ggplot(aes(x = estimate)) + 
  geom_density()

# construct a CI
boot_results2 |> 
  group_by(term) |> 
  summarize(
    ci_lower = quantile(estimate, 0.025),
    ci_upper = quantile(estimate, 0.975)
  )
```

