---
title: "p8105_hw6_zl2746"
author: "Ze Li"
date: "2023-11-27"
output: github_document
---

```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(readr)
library(ggplot2)
library(broom)
library(modelr)
library(purrr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
weather_df
```

```{r}
# Plot simple linear regression with tmax as the response 
# with tmin and prcp as the predictors
weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_smooth() +
  geom_point()

weather_df |> 
  ggplot(aes(x = prcp, y = tmax)) + 
  geom_smooth() +
  geom_point()
```


```{r}
model_slr1 = lm(tmax~tmin, weather_df)
summary(model_slr1)
model_slr2 = lm(tmax~prcp, weather_df)
summary(model_slr2)
```


Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities. Plot the distribution of your estimates, and describe these in words.

Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r̂ 2 and log(β̂ 0∗β̂ 1). 

* tmax as the response & tmin as the predictors

```{r}
# Start with a lil function
boot_sample = function(df) {
  
  sample_frac(df, replace = TRUE)
  
}

# Draw 5000 samples and analyze them
# Do the lm fit.
boot_results = 
  tibble(strap_number = 1:5000) |> 
  mutate(
    strap_sample = map(strap_number, \(i) boot_sample(weather_df)),
    models = map(strap_sample, \(df) lm(tmax ~ tmin, data = df)),
    results = map(models, broom::tidy)
  ) |> 
  select(strap_number, results) |> 
  unnest(results)

# try to summarize these results – get a bootstrap SE
boot_results |> 
  group_by(term) |> 
  summarize(
    se = sd(estimate)
  )

# look at the distribution
boot_results |> 
  filter(term == "tmin") |> 
  ggplot(aes(x = estimate)) + 
  geom_density()

# construct a CI
boot_results |> 
  group_by(term) |> 
  summarize(
    ci_lower = quantile(estimate, 0.025),
    ci_upper = quantile(estimate, 0.975)
  )
```

* tmax as the response & prcp as the predictors

```{r}
# Draw 5000 samples and analyze them
# Do the lm fit.
boot_results2 = 
  tibble(strap_number = 1:5000) |> 
  mutate(
    strap_sample = map(strap_number, \(i) boot_sample(weather_df)),
    models = map(strap_sample, \(df) lm(tmax ~ tmin + prcp, data = df)),
    results = map(models, broom::tidy)
  ) |> 
  select(strap_number, results) |> 
  unnest(results)

# try to summarize these results – get a bootstrap SE
boot_results2 |> 
  group_by(term) |> 
  summarize(
    se = sd(estimate)
  )

# look at the distribution
boot_results2 |> 
  filter(term == "tmin") |> 
  ggplot(aes(x = estimate)) + 
  geom_density()
ggsave("The distribution of boot result for problem 2.jpg")

# construct a CI
boot_results2 |> 
  group_by(term) |> 
  summarize(
    ci_lower = quantile(estimate, 0.025),
    ci_upper = quantile(estimate, 0.975)
  )
```

**The distribution is symmetric and unimodal, centered around 1.00, with estimates ranging roughly from 0.95 to 1.05. This suggests that the bootstrap method produced a reliable estimate for tmin with a narrow spread and precision.**

## Problem 3

```{r}
# Load and clean the data for regression analysis
birthweight <- read_csv("birthweight.csv") |>
  mutate(
    babysex = recode(babysex, "1" = "male", "2" = "female"),
    frace = recode(frace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other", "9" = "Unknown"),
    mrace = recode(mrace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other"),
    malform = recode(malform, "0" = "absent", "1" = "present")
  ) |>
  drop_na()
# negative wtgain?
```

Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

```{r}
# Propose a regression model for birthweight
model <- lm(bwt ~ gaweeks + ppbmi + blength + bhead + smoken + wtgain + babysex + frace + mrace, 
            data = birthweight)
summary(model)

birthweight_df <- birthweight |> 
  add_predictions(model) |> 
  add_residuals(model)

# Plotting residuals against fitted values
ggplot(birthweight_df, aes(x = pred, y = resid)) + 
  geom_point() + 
  geom_hline(yintercept = 0, color = "red") +
  xlab("Fitted Values") +
  ylab("Residuals")
```

* One using length at birth and gestational age as predictors (main effects only)

```{r}
model2 <- lm(bwt ~ gaweeks + blength, data = birthweight)
summary(model2)
```

* One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

```{r}
model3 <- lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex, 
             data = birthweight)
summary(model3)
```

Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

```{r}
set.seed(123)  

train1 = sample_n(model, 100)
test1 = anti_join(model, train1, by = "id")
```

